\documentclass[english,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%



% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}


\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={The N400's 3 As: Association, Automaticity, Attenuation (and Some Semantics Too)},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

 % Line numbering
  \usepackage{lineno}
  \linenumbers


\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{The N400's 3 As: Association, Automaticity, Attenuation (and Some
Semantics Too)}

  \shorttitle{N400 Association Attenuation}


  \author{Erin M. Buchanan\textsuperscript{1}, John E. Scofield\textsuperscript{2}, Nathan Nunley, \& NULL\textsuperscript{3}}

  % \def\affdep{{"", "", "", ""}}%
  % \def\affcity{{"", "", "", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Missouri State University\\
          \textsuperscript{2} University of Missouri\\
          \textsuperscript{3} University of Mississippi  }

  \authornote{
    Erin M. Buchanan, Department of Psychology, Missouri State University;
    John E. Scofield, Department of Psychology, University of Missouri,
    Columbia, MO, 65211; Nathan Nunley, University of Mississippi, P.O. Box
    1848, University, MS, 28677.
    
    Correspondence concerning this article should be addressed to Erin M.
    Buchanan, 901 S National, Springfield, MO, 65897. E-mail:
    \href{mailto:erinbuchanan@missouristate.edu}{\nolinkurl{erinbuchanan@missouristate.edu}}
  }


  \abstract{The N400 waveform carries new insight into the nature of linguistic
processing and may shed light into the automaticity of priming word
relationships. We investigated semantic and associative word pairs in
classic lexical decision and letter search tasks to examine their
differences in cognitive processing. Normed database information was
used to create orthogonal semantic and associative word relationships to
clearly define N400 waveforms and priming for these pairs. Participants
showed N400 reduction for related word pairs, both semantic and
associative, in comparison to unrelated word pairs. This finding was
consistent across both lexical decision and letter search tasks,
indicating automatic access for both types of relatedness. Non-word
pairs showed N400 waveforms that resembled unrelated word pairs,
indicating the controlled examination of non-advantageous words.
Response latency data nearly mirrored the EEG finding. Priming was found
for semantic and associative word relationships, while non-word pairs
were generally slower than unrelated word pairs.}
  \keywords{association, semantics, priming, N400, EEG, lexical decision, letter
search \\

    
  }





\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}



Semantic facilitation through priming occurs when a related cue word
speeds the processing of a following target word (Meyer \& Schvaneveldt,
1971). For example, if a person is reading about a yacht race, the word
boat is easier to process because of previous activation in semantic
memory. Research suggests that priming transpires by both automatic and
controlled processes. The automatic model proposes that related words
are linked in the brain due to overlapping features (Collins \& Loftus,
1975). Target words are activated without conscious control due to
automatic spreading activation within related cognitive networks.
Lexical and feature networks are thought to be stored separately, so
that semantic priming is the activation from the feature network feeding
back into the lexical level ({\textbf{???}}). The overlap of a second
word's semantic relatedness makes word recognition easier because it, in
essence, has already been processed. The controlled process model
proposes that people actively use cognitive strategies to connect
related words together. Neely (1991) describes both expectancy
generation and post lexical matching as ways that target word processing
may be speeded. In expectancy generation, people consciously attempt to
predict the words and ideas that will appear next, especially in
sentences. Whereas in post lexical matching, people delay processing of
the second target word so that it can be compared to the cue word for
evaluation. In both cases, the target word is quickened by its
relationship to the cue word.

Traditionally, priming has been tested with a simple word or nonword
decision called a lexical decision task. Participants are shown a cue or
priming word, followed by a related or unrelated target word for the
word/nonword judgment. Priming occurs when the judgment for the target
is speeded for related pairs over unrelated pairs. Lexical decision
tasks have been criticized for their inability to distinguish between
automatic and controlled processing, so both single presentation lexical
decision tasks and masked priming manipulations have been introduced to
negate controlled processing (Ford, 1983). In a single lexical decision
task, participants assess both the cue and target word so that they are
not as overtly paired together. Experimenters might also mask or distort
the cue word, so that participants do not believe they can perceive the
cue word. Even though words are garbled, word perception occurs at a
subliminal level and often facilitates the target word with automatic
activation.

\subsection{Priming in the Brain}\label{priming-in-the-brain}

Event related potentials (ERPs) are used to distinguish both the nature
of priming and the automaticity of priming. The use of ERPs is
advantageous, measuring brain activity per an electroencephalogram (EEG)
with good temporal resolution, and is thought to be a sensitive measure
of real-time language processing (Kutas \& Federmeier, 2000). The N400
is a negative waveform that occurs 400 msec after the participant is
presented with a stimulus (Brown \& Hagoort, 1993). The N400 has been
described as a \enquote{contextual integration process}, in which
meanings of words are integrated and functions, bridging together
sensory information and meaningful representations (Kutas \& Federmeier,
2000). The amplitude of the N400 is sensitive to contextual word
presentations, varying systematically with semantic processing. This
change justifies the use of the N400 as an appropriate dependent measure
for lexical decision tasks. When presented with related words, there is
an attenuation of the N400, meaning a more positive waveform when
compared to unrelated word presentation. This difference in waveforms
indicates a lessened contextual integration process because word
meanings are already activated.

Multiple theories of the N400, however, have been proposed and debated
on what explicitly the N400 indexes. On one hand, processes associated
with the N400 are believed to occur post-word recognition. Brown and
Hagoort (1993) examined a lexical decision task paired with masked
priming. No differences were found in the N400 wave between related and
unrelated words in the masked prime condition. Brown and Hagoort (1993)
concluded that this finding indicated that semantic activation was a
controlled process, because attenuation only occurred when words were
known. Thus, an \enquote{integrating} process transpires with semantic
information from of multi-word characteristic representations (Hagoort,
Baggio, \& Willems, 2009; Kutas \& Federmeier, 2011). This condition
supposedly rules out automatic processes, because the masked prime
condition only allowed automatic processes to take place. Masked priming
did not allow the participants to consciously name the prime words they
had seen; thus, they were not able to purposefully employ conscious
cognitive strategies in processing these words. However, Deacon, Hewitt,
Yang, and Nagata (2000) have found that with shorter stimulus onset
asynchronies (SOAs), this effect of masked priming disappears. SOAs are
the time interval between the prime word presentation and the target
word appearance. Short SOAs are thought to only allow for automatic
processing because the controlled, attention based processing has not
had time yet to occur. Their study showed the masked primes long enough
to enhance priming, while remaining imperceptible. With these
modifications, Deacon, Dynowska, Ritter, and Grose-Fifer (2004) found
equal N400 attenuation for the masked and unmasked primes. This result
would indicate that automatic activation was taking place, as the masked
prime condition did not allow controlled processes to take place.
({\textbf{???}}) has found similar results in the N400 using different
masking levels, which kept judgment ability of prime words below chance.

A separate theory suggests that N400 effects are seen pre-word
recognition. The N400 was found to be sensitive to pseudo- or non-words,
even when absent a resemblance to real word counterparts. Deacon et al.
(2004) explain that this result could imply processes that precede word
recognition, such as orthographic or phonological analysis. More
recently, Federmeier and Laszlo (2009) suggested that the N400 indexes
access to semantic memory. Meaningful stimuli representing a multitude
of modalities indicates a sensitivity with attention, albeit still can
occur in its absence. Processing from modalities can integrate, yielding
different meanings from different contexts, respectively (Federmeier \&
Laszlo, 2009). Regardless of competing aspects as to what the N400 is
estimated to index, vital insights have been made crossing different
cognitive domains, with the N400 illuminating aspects originating from
these different domains (Kutas \& Federmeier, 2011).

Rolke, Heil, Streb, and Hennighausen (2001) used the attention blink
rapid serial visual presentation (RSVP) paradigm, in which participants
identified target words within a stream of distractor words presented in
a different color. By selecting items via specifying the row and column
within a matrix, participants identified the target word they had
previously seen. These studies compare to masked priming, and show
automatic activation of semantic information even when targets were
missed (Rolke et al., 2001).

Letter search tasks also reduce semantic priming by focusing attention
on the lexical level instead of a feature meaning level (Friedrich,
Henik, \& Tzelgov, 1991). In this task, participants are asked to
determine if cue and target words contain a specific letter presented.
({\textbf{???}}) stipulate that this eliminated or reduced priming
indicates non-automatic semantic priming. However, it is also important
to note that Tse and Neely (2007) did yield evidence that letter search
primes produced semantic priming for low-frequency targets, albeit not
for high-frequency targets. In Smith and Besner (2001) letter search and
lexical decision combined study, they found that the letter search task
eliminated semantic priming when compared to unrelated word pairs and
the lexical decision task. Yet, Marí-Beffa, Valdés, Cullen, Catena, and
Houghton (2005) found ERP evidence for semantic processing of the prime
word during letter search tasks with the attenuation of the N400.

\subsection{Association}\label{association}

From a theoretical standpoint, the relation between associative and
semantic processing follows a deep line of research. Associative word
pairs are words that are linked in one's memory by contextual
relationships, such as basket and picnic (Nelson, McEvoy, \& Schreiber,
2004). Another example would be a word pair like alien and predator,
which would be associatively linked for Americans due to the movies and
popular culture. Semantic word pairs are those linked by their shared
features and meaning, such as \emph{wasp} and \emph{bee} (Buchanan,
Holmes, Teasley, \& Hutchison, 2013; McRae, Cree, Seidenberg, \&
McNorgan, 2005; Vinson \& Vigliocco, 2008).

Associative and semantic relationships between words are experimentally
definable by the use of normed databases. Maki, McKinley, and Thompson
(2004) took the online dictionary, WordNet ({\textbf{???}}), and used
software by ({\textbf{???}}) to create a database of words displaying
the semantic distance between individual words. This database displays
the relatedness between two words by measuring how semantically close
words appear in hierarchy, or the JCN (Jiang \& Conrath, 1997). JCN
measures the word pairs' informational distance from one another, or
their semantic similarities. Therefore, a low JCN score demonstrates a
close semantic relationship. Additionally, we can use a measure of
semantic feature overlap to examine the semantic relatedness between
word pairs (Buchanan et al., 2013; McRae et al., 2005; Vinson \&
Vigliocco, 2008), and this measure is factorally related to JCN as a
semantic measure (Maki \& Buchanan, 2008). Another useful database,
created by Nelson et al. (2004), is centered on the associative
relationships between words. Participants were given cue words and asked
to write the first word that came to mind. These responses were asked of
and averaged over many participants. The probability of a cue word
eliciting the target word is called the forward strength (FSG). For
example, when participants are shown the word \emph{lost}, the most
common response is \emph{found}, which has a FSG of .75 or occurs about
75\% of the time.

\subsection{Separating Semantic and Associative
Priming}\label{separating-semantic-and-associative-priming}

A meta-analytic review from Lucas (2000) examined semantic priming in
the absence of association. Effect sizes for semantic priming alone were
lower than associative priming. However, with the addition of an
associative relationship to an existing semantic relationship, priming
effects nearly doubled, also known as the associative boost (Moss,
Ostrin, Tyler, \& Marslen-Wilson, 1995). This result suggests that
semantic relationships, that concurrently have associations, can
increase priming effects. Priming effects, therefore, are suggested not
to be based on association in isolation. Hutchison (2003) argues against
Lucas, suggesting positive evidence for associative priming. Automatic
priming was sensitive to associative strength as well as feature
overlap. These points of contention provide impetus for more research
centering on distinctions between associative and semantic priming.

With the databases described above, orthogonal word pair stimuli can be
created to examine associative and semantic priming individually and
indeed, priming can be found for each relation separately (Buchanan,
2010). Few studies have directly compared associative and semantic
relationships, especially focusing on the brain. Deacon et al. (2004)
claim that hemispheric differences exist in lexico-semantic
representation, comparing associative and semantic priming. Deacon et
al. concluded that semantic features are localized in the right
hemisphere, whereas association is localized more within the left
hemisphere of the brain. The current study, with an aim to elaborate on
basic theoretical questions such as the relationship between associative
and semantic processing, examined the relationship between N400
activation, priming task, and word relationship type. Participants were
given both a single lexical decision and letter search task, along with
separate semantic, associative, and unrelated word pairs. We expected
that the N400 modulation might vary from the different types of word
relation, which would indicate differences in c ognitive processing and
word organization.

\section{Method}\label{method}

\subsection{Participants}\label{participants}

Twenty undergraduate students were recruited from the University of
Mississippi (thirteen women and seven men), and all volunteered to
participate. All participants were English speakers. The experiment was
carried out with the permission of the University's Institutional Review
Board, and all participants signed corresponding consent forms. One
participant's data was corrupted and could not be used, and another
participant was excluded for poor task performance (below chance),
leaving eighteen participants (twelve women and six men).

\subsection{Apparatus}\label{apparatus}

The system used was a 32 Channel EEG Cap connected to a NuAmps monopolar
digital amplifier, which was connected to a computer running SCAN 4.5
software to record the data. The SCAN software was capable of managing
continuous digital data captured by the NuAmps amplifier. STIM2 was used
to coordinate the timing issues associated with Windows operating system
and collecting EEG data on a separate computer. STIM2 also served as the
software base for programming and operating experiments of this nature.
The sensors in the EEG cap were sponges injected with 130 ml of
electrically conductive solution (non-toxic and non-irritating). Also,
to protect the participants and equipment, a surge protector was used at
all times during data acquisition. The sensors recorded electrical
activity just below the scalp, displaying brain activation. This data
was amplified by the NuAmps hardware, and processed and recorded by the
SCAN software.

\subsection{Materials}\label{materials}

This experiment consisted of 360 word pairs separated into levels in
which the target words were unrelated to the prime (120), semantically
associated to the prime (60), associatively related to the prime (60),
or were nonwords (120). We used only a small number of related word
pairs to try to reduce expectancy effects described in the introduction
(Neely, 1991). These 360 pairs were split evenly between the lexical
decision and letter search task, therefore, each task contained 60
unrelated pairs, 30 semantically related pairs, 30 associatively related
pairs, and 60 nonword pairings. The ratio of yes/no correct answers for
words and nonwords in the lexical decision task was 2:1 and 1:1 yes/no
decisions in the letter search task. Splitting the nonword pairs over
both the letter search and lexical decision task created a higher yes/no
ratio for the lexical decision task, which was controlled for by mixing
both tasks together.

The stimuli were selected from the Nelson et al. (2004) associative word
norms and Maki et al. (2004) semantic word norms. The associative word
pairs were chosen using the criteria that they were highly associatively
related, having an FSG score greater than .5; with little or no semantic
similarities, determined by having a JCN score of greater than 20. An
example of an associative pair would be \emph{dairy-cow}. The semantic
word pairs were chosen using the criteria that they had a high semantic
relatedness shown in a JCN of 3 or less; and were not associatively
related, having an FSG of less than .01 (e.g., \emph{inn-lodge}). The
unrelated words were chosen so that they had no similarities (were
unpaired in the databases), such as \emph{blender} and \emph{compass.}
For non-word pairs, the target word had one letter changed so that it no
longer represented a real word, yet the structure was left intact to
require that the participant process the word cognitively. Essentially,
non-words were orthographically similar to its real word counterpart,
except for the change in a single letter. For example, the word
\emph{pond} can be changed to \emph{pund} to produce a non-word target.
All materials and their database values can be found at our Open Science
Foundation page: \url{https://osf.io/h5sd6/}.

\subsection{Procedure}\label{procedure}

Testing occurred in one session consisting of six blocks of acquired
data, broken up by brief rest periods. Before each participant was
measured, the system was configured to the correct settings, and the
hardware prepared. Two reference channels, which define zero voltage,
were placed on the right and left mastoid bones.

We modeled the current task after Smith and Besner (2001) lexical
decision and letter search task combination. Smith and Besner (2001)
used a choice task procedure, where the color of the target word
indicated the target task. One color denoted lexical decision with
another color denoting letter search. The lexical decision task involved
participants observing a word onscreen and deciding whether or not it
was a word or non-word (such as \emph{tortoise} and \emph{werm}).
Nonrelated word pairs were created by taking prime and target words from
related pairs and randomly rearranging them to eliminate relationships
between primes and targets. The letter search task involved participants
observing a word onscreen and deciding whether it contained a repeated
letter or not (i.e.~the repeated letters in \emph{doctor} versus no
repeated letters in \emph{nurse}). Words were presented onscreen, and
would stay there until the participant pressed the corresponding keys
for yes and no. Participant responses were time limited and truncated to
60 seconds. The 1 and 9 keys were used on the number row of the
keyboard, in the participant's lap to help eliminate muscle movement
artifact in the data.

Participants were first given instructions on how to perform the lexical
decision task, followed by 15 practice trials. Next, they were given
instructions on how to judge the letter search task, followed by 15
practice trials. Participants were then given a practice session with
both letter search and lexical decision trials mixed together. Trials
were color coded for the type of decision participants had to complete
(i.e.~letter search was green, while lexical decision was red). The
experiment made use of six sets of 60 randomly assigned word pairs for a
total of 360 trials. These trials were presented in Arial 19-point font,
and the inter-trial interval was set to two seconds to allow complete
recording of the N400 waveform. Trials were recorded in five minute
blocks, and between blocks participants were allowed to rest to prevent
fatigue. The current task differed from Smith and Besner (2001) in that
participants responded to every word (prime and targets), instead of
only targets. Therefore, there was no typical fixed stimulus onset
asynchrony (SOA) because participant responses were self-paced.

\section{Results}\label{results}

\subsection{N400 Waveform Analysis}\label{n400-waveform-analysis}

\subsubsection{Data Screening and Analysis
Plan}\label{data-screening-and-analysis-plan}

The data were cleared of artifact data using EEGLAB, an open source
MATLAB tool for processing electrophysiological data. The program
automatically scanned for and removed artifacts caused by eye-blinking.
Next, the datasets were visually inspected and any remaining corrupted
sections were removed manually. Ninety percent of the data was retained
across all trials and stimulus types after muscular artifact data were
removed. However, a loss rate of 20-30 percent is not uncommon,
especially with older EEG systems. The data were combined by task and
stimulus type exclusively for the second word in each pair. Five sites
were chosen to examine priming for nonwords, associative and semantic
word pairs based on a survey of the literature. Fz, FCz, Cz, CPz, and Pz
were used from the midline. Oz was excluded due to equipment problems
across all participants. Using MATLAB, the N400 area under the curve was
calculated for each electrode site, stimulus, and task (averaging over
trials) around 300-500 msec after stimuli presentation. A constant score
was subtracted from all EEG points to ensure all curves were below zero
for area under the curve calculations.

Van Selst and Jolicoeur (1994) describes outlier elimination procedures
can be affected by factors such as sample size or data skewness. They,
as well as ({\textbf{???}}), describe procedures for adaptive outlier
criteria based on sample size to correct for this any bias due to sample
size. We utilized a non-recursive procedure with a moving criterion for
outlier elimination. For example, traditional outlier identification may
be based on a \emph{z}-score criteria of two or more standard deviations
away from the mean score. In the Van Selst and Jolicoeur (1994), this
cut-off \emph{z}-score is adjusted by sample size, and therefore, we
used the average of their recommendations for 15 to 20 participants,
\(z_{critical}\) = 2.36. The non-recursive procedure involves only
examing the data once for outliers, rather than continuing to screen for
outliers iteratively until no outliers remained. Across 18 participants
by five sites, four outlying data points were identified and
subsequently removed from further analysis. Data were also screened for
parametric assumptions of linearity, normality, homogeneity, and
homoscedasticity. The data were slightly negatively skewed, but with the
large quantity of data for each participant as well as the choice of
analysis, test statistics should be robust to this slight skew.

To analyze this data, we used multilevel models (MLM) to control for
correlated error due to repeated measures of sites and stimulus type for
each participant ({\textbf{???}}). These models were calculated using
the \emph{nlme} package in \emph{R} ({\textbf{???}}). First, a model
with only the intercept was compared to a model with participants as a
random intercept factor. Random intercepts allow each participant to
have different average scores for areas under the curve or peak latency
(see below). If the random intercept model was better than the intercept
only model, then all forthcoming models would include participants as a
random intercept factor. Models were compared only to the previous step
and were deamed \enquote{significant} if the likelihood ratio difference
score, \(\Delta\chi^2\) was greater than to be expected given the change
in degrees of freedom between models. Therefore, the \emph{p}-values for
each \(\Delta\chi^2\) were calculated based on \(\Delta df\), and
\(\alpha\) was set to .05. The two tasks, lexical desicion and letter
search, were analyzed in separate models with the area under the curve
as the dependent variable. The independent variables included the dummy
coded site location as a control variable, followed by stimulus type
coded as a dummy variable. In this analysis, we wished to compare each
stimulus type to every other stimulus type, and therefore, we set
\(\alpha\) for these six comparisons to .05/6 = .008. The stimuli
variable was recoded to examine all pairwise comparisons.

\subsubsection{Lexical Decision Task}\label{lexical-decision-task}

\subsubsection{Letter Search Task}\label{letter-search-task}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:area-table-model}Area under curve model statistics}
\begin{tabular}{lcccccc}
\toprule
Model & $df$ & AIC & BIC & $\chi^2$ & $\Delta\chi^2$ & $p$\\
\midrule
LDT Intercept & 2 & 5,653.09 & 5,660.86 & -2,824.55 & NA & NA\\
LDT Random Intercept & 3 & 5,589.29 & 5,600.94 & -2,791.65 & 65.80 & < .001\\
LDT Full & 10 & 5,509.56 & 5,548.39 & -2,744.78 & 93.73 & < .001\\
LST Intercept & 2 & 5,570.98 & 5,578.74 & -2,783.49 & NA & NA\\
LST Random Intercept & 3 & 5,494.37 & 5,506.00 & -2,744.18 & 78.62 & < .001\\
LST Full & 10 & 5,424.68 & 5,463.46 & -2,702.34 & 83.68 & < .001\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\textit{Note.} AIC: Aikaike Information Criterion, BIC: Bayesian Information Criterion
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:area-table-est}Area under curve model estimates}
\begin{tabular}{lccccc}
\toprule
Task & Predictor & $b$ & $SE$ & $t$ & $p$\\
\midrule
LDT & CZ & -28.37 & 80.83 & -0.35 & .726\\
LDT & FCZ & 62.86 & 80.83 & 0.78 & .437\\
LDT & FZ & 50.87 & 80.83 & 0.63 & .530\\
LDT & PZ & 89.80 & 80.83 & 1.11 & .267\\
LDT & Unrelated - Nonword & -137.61 & 72.24 & -1.90 & .058\\
LDT & Unrelated - Semantic & 504.04 & 72.24 & 6.98 & < .001\\
LDT & Unrelated - Associative & 348.64 & 72.24 & 4.83 & < .001\\
LDT & Nonword - Semantic & 641.65 & 72.03 & 8.91 & < .001\\
LDT & Nonword - Associative & 486.26 & 72.03 & 6.75 & < .001\\
LDT & Semantic - Associatve & -155.39 & 72.03 & -2.16 & .032\\
LST & CZ & -53.33 & 74.68 & -0.71 & .476\\
LST & FCZ & -121.96 & 74.68 & -1.63 & .103\\
LST & FZ & -109.88 & 74.95 & -1.47 & .144\\
LST & PZ & -37.85 & 74.95 & -0.50 & .614\\
LST & Unrelated - Nonword & 60.96 & 67.15 & 0.91 & .365\\
LST & Unrelated - Semantic & 456.86 & 66.55 & 6.86 & < .001\\
LST & Unrelated - Associative & 489.32 & 66.55 & 7.35 & < .001\\
LST & Nonword - Semantic & 395.90 & 67.15 & 5.90 & < .001\\
LST & Nonword - Associative & 428.36 & 67.15 & 6.38 & < .001\\
LST & Semantic - Associatve & 32.46 & 66.55 & 0.49 & .626\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\textit{Note.} The site control level was consider CPZ. Degrees of freedom are 334 for lexical decisions tasks and 332 for letter search tasks.
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\subsection{N400 Peak Analysis}\label{n400-peak-analysis}

\emph{Lexical Decision Task}. After each set was processed as described
in the data processing section, a multilevel. These stimuli were then
tested with a single sample t-test comparing each processing difference
from zero. The following hypotheses were examined. First, non-word pairs
may show significantly more negative waveforms (more negative area) due
to the need to search the lexicon before a decision can be made. Second,
semantic word paris will have significantly positive values because
priming will decrease the need to search the mental lexicon. This is
more consistent with the view that the N400 indexes initial contact with
semantic memory (Kutas \& Federmeier, 2011). Third, associative word
paris may have significantly different values from unrelated word pairs,
but a direction is not predicted. More positive values would indicate
automatic activation similar to semantics, while more negative values
would indicate a need to search the mental lexicon. Figure 1 depicts the
N400 curves for the selected electrode sites, and Table 1 presents
t-test values for the following conclusions. Nonwords were not found to
be significantly more negative than unrelated word pairs, which may
indicate a controlled lexicon search for both types of stimuli. Both
associative and semantic N400 attenuation were found across frontal and
midline sites, while neither CPz nor associative Pz showed reduction. In
Figure 1, associative and semantic N400 waveforms are well above the
unrelated word pairs, indicating automatic priming for both types of
relatedness, even when stimuli are controlled for opposing
relationships.

\emph{Letter Search Task}. The same five sites were analyzed as the
lexical decision task. Again, data were subtracted from unrelated word
pairs averages and then compared against zero with single sample
t-tests. The following hypotheses were expected. First, ? Since task
demands require a focus at the lexical level, nonword pairings should
not show significant differences from unrelated word pairs. However, if
word processing is automatic in a letter search task ({\textbf{???}}),
then nonwords pairs may show more negative waveforms as participants
search the lexicon for the word pair. Second, ? Semantic and associative
word pairs may have significantly positive values because priming will
decrease the need to search the mental lexicon; however some research
literature indicates that letter search tasks eliminate semantic priming
(Smith \& Besner, 2001). Positive values would indicate a priming
effect, which is evidence for activation spreading automatically within
the mental lexicon. More negative or nonsignficant values would indicate
processing at the lexical, but not semantic, level. Figure 2 portrays
the N400 waveforms for the letter search task, and Table 2 contains the
t-test values for the following conclusions. Although the average
nonword waveform appears to be much lower than unrelated waveform at
many sites, the variance across subjects was very large, and no
significant differences were found. This finding could indicate that
?wordness? did not matter since participants were searching at a lexical
level for specific letters. Nearly all sites showed significant
associative and semantic attenuation for the N400 waveform, semantic Cz
being the only exception. In comparison, this result seems to suggest
that letter search does not inhibit automatic activation of word meaning
and association. The nonsignificant relationship between nonwords and
unrelated word pairs could be either statistical power or a controlled
search process, regardless of task demands.

\subsection{Task Performance}\label{task-performance}

Task data were analyzed for correctness in the lexical decision and
letter search tasks individually. Error rates were tested with a 2X4
(task by stimulus) repeated measures ANOVA. Overall, performance in the
letter search task (M=.97, SD=.02) was equal to the lexical decision
task (M=.97, SD=.02), F(1,13)=1.54, p=.24. The interaction between task
type and stimuli was also not significant F(3,39)=1.74, p=.18. The
different types of stimuli showed a difference in performance,
F(3,39)=9.85, p\textless{}.001, between nonwords (M=.94, SD=.03,
t(13)=-3.02, p=.01) and unrelated word pairs (M=.97, SD=.01); nonwords
and associative word pairs (M=.98, SD=.01, t(14)=-5.55,
p\textless{}.001); and nonwords and semantic word pairs (M=.98, SD=.02,
t(14)=-3.45, p=.01). The other stimuli comparisons were all
non-significant, and averages by task can be provided upon request.

\subsection{Reaction Time Performance}\label{reaction-time-performance}

Reaction time data were excluded for incorrect trials. Average reaction
times were calculated for each task type and stimulus. The Van Selst and
Jolicoeur (1994) 3 standard deviation outlier trimmer procedure was used
to eliminate very long reaction times. Next, associative, semantic, and
nonword conditions were subtracted from their matching unrelated word
conditions. Figure 4 depicts the priming differences for each condition.
Each stimulus difference was analyzed with a single sample t-test
against zero to examine for priming.

\emph{Letter Search Task}. All conditions in the letter search task were
significantly primed over unrelated words pairs, while nonwords were
significantly slower than unrelated word pairs. As shown in Figure 4,
associative words pairs were almost 200 msecs faster than unrelated word
pairs, t(17) = 3.54, p \textless{} .01, and semantic word pairs were
also around 200 msecs faster than unrelated word pairs, t(17) = 6.38,
p\textless{}.01. Nonwords were significantly slower than unrelated word
pairs by about 200 msecs, t(17) = -5.18, p\textless{}.01. Given previous
research, it was slightly surprising that semantic word pairs would be
primed during a letter search task, however, the current word list has
also shown this effect in Buchanan (2010), and this effect matches N400
results.

\emph{Lexical Decision Task}. Priming was found for associative word
pairs in the lexical decision task, a marginal effect semantic word
pairs, and slowing for non-word pairs when compared to unrelated word
pairs. Associations were about 120 msecs faster than unrelated word
pairs, t(17) = 2.99, p\textless{}.01. Semantic word pairs were primed
approximately 85 msecs over unrelated pairs, which approached
significance, t(17) = 1.93, p=.07. Semantic priming was expected in the
lexical decision task, and this effect was most likely due to our small
sample size. Nonwords were again 200 msecs slower than unrelated word
pairs, t(17) = -5.24, p\textless{}.01.

\section{Discussion}\label{discussion}

These experiments were designed to explore the differences between N400
activation in the brain following presentation of semantic-only,
associative-only, and unrelated word pairs in priming tasks. The N400
data and reaction time data present picture of associative and semantic
priming during both lexical decision and letter search task. Because
both tasks were designed to reduce controlled processing of cue-target
relationships, these findings imply automatic activation of word
meanings and associations, even when task demands do not warrant word
activation. Nonword activation is more problematic to interpret, as N400
waveforms are not different from unrelated word pairs, but reaction time
data is much slower. These results, taken together, may illustrate a
controlled process search of the lexicon requiring the same activation
levels. When an unrelated target word is found in the lexicon,
controlled search is terminated, while searching for a nonword continues
for more time before the search is terminated. However, Deacon et al.
(2000) point to potential issues with the relationship between the N400
and automaticity. Semantic processing, Deacon et al. (2000) discuss, is
possible in the absence of attention or a dearth of awareness.

Since findings were roughly similar for associative and semantic word
pairs, we can postulate that the activation processes for these types of
word relatedness are also roughly similar. This experiment cannot
separate if the cognitive architecture is different for associations and
semantics, but that the automatic mechanisms for priming are comparable.
One limitation is that the long stimulus onset times may have allowed
for controlled processing in the reaction time data, but the consistent
N400 attenuation suggests a quick search of the lexicon similar to an
automatic activation process. Finally, differences in activation across
gender need to be explored. Although not conclusive due to sample size,
we found that male activation across stimuli was implicated in
traditional left Broca?s area, while female activation averaged to
central parietal areas. Regardless of any potential differences, the
broad sensitivity of the N400 means it can be implemented when
investigating how information is stored in the brain. The temporal lobe
has been shown to be implicated as a source from the N400, albeit occurs
in a flexible manner, varying with different classes of stimuli
(Federmeier \& Laszlo, 2009). There are sometimes dissociations between
the N400 and reaction time measures. The use of the N400 can therefore
be seen as an especially relevant dependent measure for the reason that
components can only partially be a reflection of semantic processes
relating to response latencies (Kutas \& Federmeier, 2011).

To date, research has focused on semantic priming and its automaticity
without many controls for associative relationships embedded in word
pairs. Certainly there is overlap between meaning and context use of
words, but these differences can be studied separately using available
databases (Hutchison, 2003). Our current study has supported findings by
({\textbf{???}}), who showed activation during letter search tasks,
along with the many studies on automatic activation during masked
priming (Deacon et al., 2000; Kiefer, 2002).

Limitations do exist within these experiments. As previously mentioned a
larger sample size would increase the power coefficient of the findings.
Future studies should focus on the extent of priming in semantic word
pairs during a letter search task, which is a controversial topic within
the literature. Since our study limited relatedness to associations or
semantics, upcoming experiments could examine the interaction between
word relationship type of N400 attenuation. Kreher, Holcomb, and
Kuperberg (2006) have shown that N400 waveform differences can be
attributed to different strengths of semantic relatedness in a linear
fashion. With more exploration into the exact priming nature of
associations and semantics, we may begin to discover their cognitive
mechanisms.

\newpage

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-Brown1993}{}
Brown, C., \& Hagoort, P. (1993). The processing nature of the N400:
Evidence from masked priming. \emph{Journal of Cognitive Neuroscience},
\emph{5}(1), 34--44.
doi:\href{https://doi.org/10.1162/jocn.1993.5.1.34}{10.1162/jocn.1993.5.1.34}

\hypertarget{ref-Buchanan2010}{}
Buchanan, E. M. (2010). Access into Memory: Differences in Judgments and
Priming for Semantic and Associative Memory. \emph{Journal of Scientific
Psychology}, (March), 1--8.

\hypertarget{ref-Buchanan2013}{}
Buchanan, E. M., Holmes, J. L., Teasley, M. L., \& Hutchison, K. A.
(2013). English semantic word-pair norms and a searchable Web portal for
experimental stimulus creation. \emph{Behavior Research Methods},
\emph{45}(3), 746--757.
doi:\href{https://doi.org/10.3758/s13428-012-0284-z}{10.3758/s13428-012-0284-z}

\hypertarget{ref-Collins1975}{}
Collins, A. M., \& Loftus, E. F. (1975). A spreading-activation theory
of semantic processing. \emph{Psychological Review}, \emph{82}(6),
407--428.
doi:\href{https://doi.org/10.1037//0033-295X.82.6.407}{10.1037//0033-295X.82.6.407}

\hypertarget{ref-Deacon2004}{}
Deacon, D., Dynowska, A., Ritter, W., \& Grose-Fifer, J. (2004).
Repetition and semantic priming of nonwords: Implications for theories
of N400 and word recognition. \emph{Psychophysiology}, \emph{41}(1),
60--74.
doi:\href{https://doi.org/10.1111/1469-8986.00120}{10.1111/1469-8986.00120}

\hypertarget{ref-Deacon2000}{}
Deacon, D., Hewitt, S., Yang, C.-M., \& Nagata, M. (2000). Event-related
potential indices of semantic priming using masked and unmasked words:
evidence that the N400 does not reflect a post-lexical process.
\emph{Cognitive Brain Research}, \emph{9}(2), 137--146.
doi:\href{https://doi.org/10.1016/S0926-6410(99)00050-6}{10.1016/S0926-6410(99)00050-6}

\hypertarget{ref-Federmeier2009}{}
Federmeier, K. D., \& Laszlo, S. (2009). Time for meaning:
Electrophysiology provides insights into dynamics of representation and
processing in semantic memory. In B. H. Ross (Ed.), \emph{Psychology of
learning and motivation} (pp. 1--44). Burlington, MA: Academic Press.

\hypertarget{ref-Ford1983}{}
Ford, M. (1983). A method for obtaining measures of local parsing
complexity throughout sentences. \emph{Journal of Verbal Learning and
Verbal Behavior}, \emph{22}(2), 203--218.
doi:\href{https://doi.org/10.1016/S0022-5371(83)90156-1}{10.1016/S0022-5371(83)90156-1}

\hypertarget{ref-Friedrich1991}{}
Friedrich, F. J., Henik, A., \& Tzelgov, J. (1991). Automatic processes
in lexical access and spreading activation. \emph{Journal of
Experimental Psychology: Human Perception and Performance},
\emph{17}(3), 792--806.
doi:\href{https://doi.org/10.1037//0096-1523.17.3.792}{10.1037//0096-1523.17.3.792}

\hypertarget{ref-Hagoort2009}{}
Hagoort, P., Baggio, G., \& Willems, R. M. (2009). Semantic unification.
In M. S. Gazzaniga (Ed.), \emph{The cognitive neurosciences} (4th ed.,
pp. 819--836). Cambridge, MA: MIT Press.

\hypertarget{ref-Hutchison2003}{}
Hutchison, K. A. (2003). Is semantic priming due to association strength
or feature overlap? A microanalytic review. \emph{Psychonomic Bulletin
\& Review}, \emph{10}(4), 785--813.
doi:\href{https://doi.org/10.3758/BF03196544}{10.3758/BF03196544}

\hypertarget{ref-Jiang1997}{}
Jiang, J. J., \& Conrath, D. W. (1997). Semantic similarity based on
corpus statistics and lexical taxonomy. In \emph{In proceedings of
international conference research on computational linguistics (rocling
x)}. Taiwan.

\hypertarget{ref-Kiefer2002}{}
Kiefer, M. (2002). The N400 is modulated by unconsciously perceived
masked words: further evidence for an automatic spreading activation
account of N400 priming effects. \emph{Cognitive Brain Research},
\emph{13}(1), 27--39.
doi:\href{https://doi.org/10.1016/S0926-6410(01)00085-4}{10.1016/S0926-6410(01)00085-4}

\hypertarget{ref-Kreher2006}{}
Kreher, D. A., Holcomb, P. J., \& Kuperberg, G. R. (2006). An
electrophysiological investigation of indirect semantic priming.
\emph{Psychophysiology}, \emph{43}(6), 550--563.
doi:\href{https://doi.org/10.1111/j.1469-8986.2006.00460.x}{10.1111/j.1469-8986.2006.00460.x}

\hypertarget{ref-Kutas2000}{}
Kutas, M., \& Federmeier, K. D. (2000). Electrophysiology reveals
semantic memory use in language comprehension. \emph{Trends in Cognitive
Sciences}, \emph{4}(12), 463--470.
doi:\href{https://doi.org/10.1016/S1364-6613(00)01560-6}{10.1016/S1364-6613(00)01560-6}

\hypertarget{ref-Kutas2011}{}
Kutas, M., \& Federmeier, K. D. (2011). Thirty years and counting:
Finding meaning in the N400 component of the Event-Related Brain
Potential (ERP). \emph{Annual Review of Psychology}, \emph{62}(1),
621--647.
doi:\href{https://doi.org/10.1146/annurev.psych.093008.131123}{10.1146/annurev.psych.093008.131123}

\hypertarget{ref-Lucas2000}{}
Lucas, M. (2000). Semantic priming without association: A meta-analytic
review. \emph{Psychonomic Bulletin \& Review}, \emph{7}(4), 618--630.
doi:\href{https://doi.org/10.3758/BF03212999}{10.3758/BF03212999}

\hypertarget{ref-Maki2008}{}
Maki, W. S., \& Buchanan, E. M. (2008). Latent structure in measures of
associative, semantic, and thematic knowledge. \emph{Psychonomic
Bulletin \& Review}, \emph{15}(3), 598--603.
doi:\href{https://doi.org/10.3758/PBR.15.3.598}{10.3758/PBR.15.3.598}

\hypertarget{ref-Maki2004}{}
Maki, W. S., McKinley, L. N., \& Thompson, A. G. (2004). Semantic
distance norms computed from an electronic dictionary (WordNet).
\emph{Behavior Research Methods, Instruments, \& Computers},
\emph{36}(3), 421--431.
doi:\href{https://doi.org/10.3758/BF03195590}{10.3758/BF03195590}

\hypertarget{ref-Mari-Beffa2005}{}
Marí-Beffa, P., Valdés, B., Cullen, D. J., Catena, A., \& Houghton, G.
(2005). ERP analyses of task effects on semantic processing from words.
\emph{Cognitive Brain Research}, \emph{23}(2-3), 293--305.
doi:\href{https://doi.org/10.1016/j.cogbrainres.2004.10.016}{10.1016/j.cogbrainres.2004.10.016}

\hypertarget{ref-McRae2005}{}
McRae, K., Cree, G. S., Seidenberg, M. S., \& McNorgan, C. (2005).
Semantic feature production norms for a large set of living and
nonliving things. \emph{Behavior Research Methods}, \emph{37}(4),
547--559.
doi:\href{https://doi.org/10.3758/BF03192726}{10.3758/BF03192726}

\hypertarget{ref-Meyer1971}{}
Meyer, D. E., \& Schvaneveldt, R. W. (1971). Facilitation in recognizing
pairs of words: Evidence of a dependence between retrieval operations.
\emph{Journal of Experimental Psychology}, \emph{90}(2), 227--234.
doi:\href{https://doi.org/10.1037/h0031564}{10.1037/h0031564}

\hypertarget{ref-Moss1995}{}
Moss, H. E., Ostrin, R. K., Tyler, L. K., \& Marslen-Wilson, W. D.
(1995). Accessing different types of lexical semantic information:
Evidence from priming. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{21}(4), 863--883.
doi:\href{https://doi.org/10.1037//0278-7393.21.4.863}{10.1037//0278-7393.21.4.863}

\hypertarget{ref-Neely1991}{}
Neely, J. H. (1991). \emph{Semantic priming effects in visual word
recognition: A selective review of current findings and theories}.
Hillsdale, NJ: Lawrence Erlbaum Associates, Inc.

\hypertarget{ref-Nelson2004}{}
Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (2004). The University
of South Florida free association, rhyme, and word fragment norms.
\emph{Behavior Research Methods, Instruments, \& Computers},
\emph{36}(3), 402--407.
doi:\href{https://doi.org/10.3758/BF03195588}{10.3758/BF03195588}

\hypertarget{ref-Rolke2001}{}
Rolke, B., Heil, M., Streb, J., \& Hennighausen, E. (2001). Missed prime
words within the attentional blink evoke an N400 semantic priming
effect. \emph{Psychophysiology}, \emph{38}(2), 165--174.
doi:\href{https://doi.org/10.1111/1469-8986.3820165}{10.1111/1469-8986.3820165}

\hypertarget{ref-Smith2001}{}
Smith, M. C., \& Besner, D. (2001). Modulating semantic feedback in
visual word recognition. \emph{Psychonomic Bulletin \& Review},
\emph{8}(1), 111--117.
doi:\href{https://doi.org/10.3758/BF03196146}{10.3758/BF03196146}

\hypertarget{ref-Tse2007}{}
Tse, C.-S., \& Neely, J. H. (2007). Semantic priming from
letter-searched primes occurs for low- but not high-frequency targets:
Automatic semantic access may not be a myth. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{33}(6),
1143--1161.
doi:\href{https://doi.org/10.1037/0278-7393.33.6.1143}{10.1037/0278-7393.33.6.1143}

\hypertarget{ref-VanSelst1994}{}
Van Selst, M., \& Jolicoeur, P. (1994). Can mental rotation occur before
the dual-task bottleneck? \emph{Journal of Experimental Psychology:
Human Perception and Performance}, \emph{20}(4), 905--921.
doi:\href{https://doi.org/10.1037/0096-1523.20.4.905}{10.1037/0096-1523.20.4.905}

\hypertarget{ref-Vinson2008}{}
Vinson, D. P., \& Vigliocco, G. (2008). Semantic feature production
norms for a large set of objects and events. \emph{Behavior Research
Methods}, \emph{40}(1), 183--190.
doi:\href{https://doi.org/10.3758/BRM.40.1.183}{10.3758/BRM.40.1.183}






\end{document}
